Supplemental Information A: Full Annotated Analysis and Reproducible Code

### 2022-10-02 Supplemental-Material-A-Annotated-Analysis.Rmd
re-render with main comments added

## Multiple Imputation

We ultimately aim to create 20 imputed data sets to perform the analyses on. As outlined by @Monden2015, we will use the key variables themselves as well as auxiliary variables to impute missing values. Auxiliary variables are any pre-, post-, or daily dairy variables other than the main variables. If there are any modeling issues we will limit the auxiliary variables to all variables that that are significantly ($p$ \< .01) and meaningfully ($r$ \> .3) correlated with (1) the key variables or (2) missingness on the key variables.

We create the imputed data set for each of the analyses. This includes the main analyses with across all three studies, using the set of common variables, as well as follow-up analyses for study-specific, interaction-specific and time scale specific data sets.

```{r varNames}
varNamS123Aux <- varNames %>%
  filter(
    aux != 0,
    studyS1 == "S1",
    studyS2 == "S2",
    studyS3 == "S3"
  ) %>%
  select(varNam) %>%
  pull
varNamS1Aux <- varNames %>%
  filter(
    aux != 0,
    studyS1 == "S1"
  ) %>%
  select(varNam) %>%
  pull
varNamS2Aux <- varNames %>%
  filter(
    aux != 0,
    studyS2 == "S2"
  ) %>%
  select(varNam) %>%
  pull
varNamS3Aux <- varNames %>%
  filter(
    aux != 0,
    studyS3 == "S3"
  ) %>%
  select(varNam) %>%
  pull

@@

@@

### Main Analysis

We begin by preparing the data for the main analysis, which combines the common variables of all three studies. Here, we:

1.  Select the variables for all relevant analysis (i.e., imputation, 3MPCA, and validation) across all three studies.
2.  Create the combined dataset in the correct format (long format with all missed time points as NAs).
3.  Impute the data and save the imputed datasets for later recall.

```{r MiMainPrep}
#################################################################
##                    Variable Name Vectors                    ##
#################################################################
varNamS123MIPsbl <- c(
  paste(varNamS123MI, rep(".pre", length(varNamS123MI)), sep = ""),
  varNamS123MI,
  paste(varNamS123MI, rep(".post", length(varNamS123MI)), sep = "")
)

varNamMiMainNoms <- varNames %>%
  filter(
    aux == 1,
    format == "nominal",
    studyS1 == "S1",
    studyS2 == "S2",
    studyS3 == "S3"
  ) %>%
  select(varNam) %>%
  pull

#################################################################
##                    Dataframe Preparation                    ##
#################################################################
dtMiMain <- rbind(
  dtS1Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S1") %>% 
    mutate(across(!TID & !study, as.numeric)),
  dtS2Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S2"),
  dtS3Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S3")
) %>%
  group_by(study, PID) %>%
  mutate(ID = cur_group_id()) %>%
  ungroup %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  rowwise() %>%
  mutate(
    InteractionDum = sum(IntergroupContact, IngroupContact, na.rm = TRUE),
    InteractionDum = if_else(InteractionDum > 0, 1, InteractionDum)
  ) %>%
  ungroup() %>%
  select(ID,
         study,
         date,
         week,
         everything(),
         -PID,
         -starts_with("ResponseId"), 
         -starts_with("roommate"),
         -starts_with("Reason")) %>%
  as.data.frame %>%
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., ID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(ID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  mutate(study = replace_na(study, calc_mode(study))) %>%
  ungroup %>%
  group_by(study, TIDnum) %>%
  mutate(across(c("date", "week", "TID"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate(across(ends_with(c(".pre", ".post")), ~ ifelse(is.nan(.), NA, .))) %>%
  as.data.frame 
```

```{r MainImp}
#################################################################
##                     Imputation Bi-daily                     ##
#################################################################
# set.seed(123)
# MiMain <-
#   amelia(
#     dtMiMain,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("TID", "date", "week", "study", "IntergroupContact", "IngroupContact"), #"PID",
#     #lags = names(dtMiMain)[!names(dtMiMain) %in% idVars],
#     #lags = names(dtMiMain)[names(dtMiMain) %in%varNamInMiMainRed],
#     #noms = names(dtMiMain)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMain))],
#     noms = c("InteractionDum"),
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiMain, file = "data/imputed/MainImputed.RData")
load("data/imputed/MainImputed.RData")

# # Stability to imputations:
# set.seed(123)
# MiMainStability <-
#   amelia(
#     dtMiMain,
#     m = 20,
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c(
#       "TID",
#       "date",
#       "week",
#       "study",
#       "IntergroupContact",
#       "IngroupContact"
#     ),
#     #lags = names(dtMiMain)[!names(dtMiMain) %in% idVars],
#     #lags = names(dtMiMain)[names(dtMiMain) %in%varNamInMiMainRed],
#     #noms = names(dtMiMain)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMain))],
#     noms = c("InteractionDum"),
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiMainStability, file = "data/imputed/MainImputedStability.RData")
load("data/imputed/MainImputedStability.RData")

##---------------------------------------------------------------
##                Restore Missingness by Design                --
##---------------------------------------------------------------

# SHOULD STILL BE DONE? 
# (remove imputed values that were missing by design. E.g., partner attitudes when there were no interactions)

### Follow-up: Studies

#### Study 1

```{r MiS1Prep}
#################################################################
##                    Variable Name Vectors                    ##
#################################################################
varNamS1MiPsbl <- c(
  paste(varNamS1MI, rep(".pre", length(varNamS1MI)), sep = ""),
  varNamS1MI,
  paste(varNamS1MI, rep(".post", length(varNamS1MI)), sep = "")
)

varNamdtS1Noms <- varNames %>%
  filter(
    aux == 1,
    format == "nominal",
    studyS1 == "S1"
  ) %>%
  select(varNam) %>%
  pull

#################################################################
##                    Dataframe Preparation                    ##
#################################################################
dtMiS1 <- dtS1Red %>% 
  select(TID, any_of(varNamS1MiPsbl)) %>% 
  mutate(across(!TID, as.numeric)) %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  select(PID,
         date,
         week,
         everything(),
         -starts_with("ResponseId")) %>%
  as.data.frame %>% 
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., PID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(PID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  ungroup %>% 
  group_by(TIDnum) %>%
  mutate(across(c("date", "week", "TID"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate(across(ends_with(c(".pre", ".post")), ~ ifelse(is.nan(.), NA, .))) %>% 
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         which(sapply(., sd, na.rm = TRUE) > 0)) %>% # only include variables that vary (i.e., sd != 0)
  as.data.frame

allDuplicated <- function(vec){
  front <- duplicated(vec)
  back <- duplicated(vec, fromLast = TRUE)
  all_dup <- front + back > 0
  return(all_dup)
}

varNamDifS1 <- names(dtMiS1)[gsub(".pre|.post|_calc", "", names(dtMiS1)) %>% allDuplicated]

# Variables removed for study 1 due to high multicollinearity:
varNamS1Out <- dtMiS1 %>%
  select(
    any_of(varNamDifS1),
    mdmq.calmness.pre_calc,
    mdmq.alertness.pre_calc,
    mdmq.valence.pre_calc,
    relatednessFrust.pre_calc,
    competenceFrust.pre_calc,
    competenceSat.pre_calc,
    relatednessSat.pre_calc,
    DutchFriends.pre,
    secNatDum.pre,
    timeNL.pre,
    stress.post,
    discrimination_month.post,
    rosenberg.post,
    qualityStar,
    starts_with("SSAS")
  ) %>%
  names

dtMiS1 <- dtMiS1 %>%
  # mutate(
  #   assimilation.dif = assimilation.post - assimilation.pre,
  #   integration.dif = integration.post - integration.pre,
  #   marginalization.dif = marginalization.post - marginalization.pre,
  #   separation.dif = separation.post - separation.pre,
  #   VIA_Dutch.dif = VIA_Dutch.post - VIA_Dutch.post,
  #   VIA_heritage.dif = VIA_heritage.post - VIA_heritage.pre,
  #   IntGrAnx.dif = IntGrAnx.post_calc - IntGrAnx.pre_calc,
  #   swl.dif = swl.post_calc - swl.pre_calc
  # ) %>% 
  select(
    -any_of(varNamS1Out)
  ) %>%
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         which(sapply(., sd, na.rm = TRUE) > 0)) %>% 
  mutate_all(~ifelse(is.nan(.), NA, .)) %>%
  as.data.frame

# lares::corr_cross(
#   dtMiS1 %>% select_if(is.numeric), # name of dataset
#   max_pvalue = 0.05, # display only significant correlations (at 5% level)
#   top = 20 # display top 20 couples of variables (by correlation coefficient)
# )
```

```{r MiS1}
#################################################################
##                     Imputation Bi-daily                     ##
#################################################################
# set.seed(123)
# MiS1 <-
#   amelia(
#     dtMiS1,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     # parallel = "multicore",
#     # ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiS1, file = "data/imputed/S1Imputed.RData")
load("data/imputed/S1Imputed.RData")

# # Imputation Stability:
# set.seed(123)
# MiS1Stability <-
#   amelia(
#     dtMiS1,
#     m = 20,
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     # parallel = "multicore",
#     # ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiS1Stability, file = "data/imputed/S1ImputedStability.RData")
load("data/imputed/S1ImputedStability.RData")
```

#### Study 2

```{r MiS2Prep}
#################################################################
##                    Variable Name Vectors                    ##
#################################################################
varNamS2MiPsbl <- c(
  paste(varNamS2MI, rep(".pre", length(varNamS2MI)), sep = ""),
  varNamS2MI,
  paste(varNamS2MI, rep(".post", length(varNamS2MI)), sep = "")
)

varNamdtS2Noms <- varNames %>%
  filter(
    aux == 1,
    format == "nominal",
    studyS2 == "S2"
  ) %>%
  select(varNam) %>%
  pull

#################################################################
##                    Dataframe Preparation                    ##
#################################################################
dtMiS2 <- 
  dtS2Red %>% 
  select(TID, any_of(varNamS2MiPsbl)) %>% 
  mutate(across(!TID, as.numeric)) %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  select(PID,
         date,
         week,
         everything(),
         -starts_with("ResponseId")) %>%
  as.data.frame %>% 
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., PID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(PID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  ungroup %>% 
  group_by(TIDnum) %>%
  mutate(across(c("date", "week", "TID"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate(across(ends_with(c(".pre", ".post")), ~ ifelse(is.nan(.), NA, .))) %>% 
  as.data.frame %>%
  mutate(date = as.character(date)) %>%
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         everything()) %>%
  select_if(function(x) is.character(x) | is.factor(x) | (is.numeric(x) && sd(x, na.rm = TRUE) > 0)) %>%
  as.data.frame

varNamDifS2 <- names(dtMiS2)[gsub(".pre|.post|_calc", "", names(dtMiS2)) %>% allDuplicated]

# # Variables removed for study 2 due to high multicollinearity:
varNamS2Out <- dtMiS2 %>%
  select(
    any_of(varNamDifS2),
    ContactDesire,
    DesireIntergroup,
    DesireIngroup,
    Reason.pre,
    # mdmq.calmness.pre_calc,
    # mdmq.alertness.pre_calc,
    # mdmq.valence.pre_calc,
    # relatednessFrust.pre_calc,
    # competenceFrust.pre_calc,
    # competenceSat.pre_calc,
    # relatednessSat.pre_calc,
    # DutchFriends.pre,
    # secNatDum.pre,
    timeNL.pre,
    starts_with("HS"),
    starts_with("Home")
    # stress.post,
    # discrimination_month.post,
    # rosenberg.post,
    # qualityStar,
    # starts_with("SSAS")
  ) %>%
  names

dtMiS2Fin <- dtMiS2 %>%
  # mutate(
  #   assimilation.dif = assimilation.post - assimilation.pre,
  #   integration.dif = integration.post - integration.pre,
  #   marginalization.dif = marginalization.post - marginalization.pre,
  #   separation.dif = separation.post - separation.pre,
  #   VIA_Dutch.dif = VIA_Dutch.post - VIA_Dutch.post,
  #   VIA_heritage.dif = VIA_heritage.post - VIA_heritage.pre,
  #   IntGrAnx.dif = IntGrAnx.post_calc - IntGrAnx.pre_calc,
  #   swl.dif = swl.post_calc - swl.pre_calc
  # ) %>%
  select(
    -any_of(varNamS2Out)
  ) %>%
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         everything()) %>%
         #which(sapply(., sd, na.rm = TRUE) > 0)) %>%
  mutate_all(~ifelse(is.nan(.), NA, .)) %>%
  as.data.frame

# lares::corr_cross(
#   dtMiS2Fin %>% select_if(is.numeric), # name of dataset
#   max_pvalue = 0.05, # display only significant correlations (at 5% level)
#   top = 20 # display top 20 couples of variables (by correlation coefficient)
# )
```

```{r s2StlTest}
# Seasonal Decomposition of Time Series by Loess

# dtMiS2 %>% 
#   select(
#     PID,
#     TIDnum,
#     AttitudesDutch
#   ) %>%
#   #filter(PID == 1) %>%
#   #na.exclude(as.ts(.)) %>%
#   as.ts %>%
#   stats::stl(., na.action=na.omit)
# 
# testLoess <- loess(AttitudesDutch ~ TIDnum, data = dtMiS2 %>% filter(PID == 1))
# testSpline <- pspline::sm.spline(dtMiS2$AttitudesDutch, dtMiS2$TIDnum)
# testMarkov <- semiMarkov()
# 
# stats::stl(dtMiS2Fin)

```{r MiS2}
#################################################################
##                     Imputation Bi-daily                     ##
#################################################################
# set.seed(123)
# MiS2 <-
#   amelia(
#     dtMiS2Fin,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiS2, file = "data/imputed/S2Imputed.RData")
#load("data/imputed/S2Imputed.RData")

# # Imputation Stability:
# set.seed(123)
# MiS2Stability <-
#   amelia(
#     dtMiS2,
#     m = 20,
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiS2Stability, file = "data/imputed/S2ImputedStability.RData")
#load("data/imputed/S2ImputedStability.RData")
```

#### Study 3

```{r MiS3Prep}
#################################################################
##                    Variable Name Vectors                    ##
#################################################################
varNamS3MiPsbl <- c(
  paste(varNamS3MI, rep(".pre", length(varNamS3MI)), sep = ""),
  varNamS3MI,
  paste(varNamS3MI, rep(".post", length(varNamS3MI)), sep = "")
)

varNamdtS3Noms <- varNames %>%
  filter(
    aux == 1,
    format == "nominal",
    studyS3 == "S2"
  ) %>%
  select(varNam) %>%
  pull

#################################################################
##                    Dataframe Preparation                    ##
#################################################################
dtMiS3 <- 
  dtS3Red %>% 
  select(TID, any_of(varNamS3MiPsbl)) %>% 
  mutate(across(!TID, as.numeric)) %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  select(PID,
         date,
         week,
         everything(),
         -starts_with("ResponseId")) %>%
  as.data.frame %>% 
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., PID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(PID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  ungroup %>% 
  group_by(TIDnum) %>%
  mutate(across(c("date", "week", "TID"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate(across(ends_with(c(".pre", ".post")), ~ ifelse(is.nan(.), NA, .))) %>% 
  as.data.frame %>%
  mutate(date = as.character(date)) %>%
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         everything()) %>%
  select_if(function(x) is.character(x) | is.factor(x) | (is.numeric(x) && sd(x, na.rm = TRUE) > 0)) %>%
  as.data.frame

varNamDifS3 <- names(dtMiS3)[gsub(".pre|.post|_calc", "", names(dtMiS3)) %>% allDuplicated]

# # Variables removed for study 2 due to high multicollinearity:
varNamS3Out <- dtMiS3 %>%
  select(
    any_of(varNamDifS3),
    # ContactDesire,
    # DesireIntergroup,
    # DesireIngroup,
    # Reason.pre,
    # mdmq.calmness.pre_calc,
    # mdmq.alertness.pre_calc,
    # mdmq.valence.pre_calc,
    # relatednessFrust.pre_calc,
    # competenceFrust.pre_calc,
    # competenceSat.pre_calc,
    # relatednessSat.pre_calc,
    # DutchFriends.pre,
    # secNatDum.pre,
    # timeNL.pre,
    # starts_with("HS"),
    # starts_with("Home")
    # stress.post,
    # discrimination_month.post,
    # rosenberg.post,
    # qualityStar,
    # starts_with("SSAS")
  ) %>%
  names

dtMiS3Fin <- dtMiS3 %>%
  # mutate(
  #   assimilation.dif = assimilation.post - assimilation.pre,
  #   integration.dif = integration.post - integration.pre,
  #   marginalization.dif = marginalization.post - marginalization.pre,
  #   separation.dif = separation.post - separation.pre,
  #   VIA_Dutch.dif = VIA_Dutch.post - VIA_Dutch.post,
  #   VIA_heritage.dif = VIA_heritage.post - VIA_heritage.pre,
  #   IntGrAnx.dif = IntGrAnx.post_calc - IntGrAnx.pre_calc,
  #   swl.dif = swl.post_calc - swl.pre_calc
  # ) %>%
  select(
    -any_of(varNamS3Out)
  ) %>%
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         everything()) %>%
  mutate_all(~ifelse(is.nan(.), NA, .)) %>%
  as.data.frame

lares::corr_cross(
  dtMiS3Fin %>% select_if(is.numeric), # name of dataset
  max_pvalue = 0.05, # display only significant correlations (at 5% level)
  top = 20 # display top 20 couples of variables (by correlation coefficient)
)
```

```{r MiS3}
#################################################################
##                     Imputation Bi-daily                     ##
#################################################################
# set.seed(123)
# MiS3 <-
#   amelia(
#     dtMiS3Fin,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiS3, file = "data/imputed/S3Imputed.RData")
#load("data/imputed/S2Imputed.RData")

# Imputation Stability:
# set.seed(123)
# MiS3Stability <-
#   amelia(
#     dtMiS3Fin,
#     m = 20,
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiS3Stability, file = "data/imputed/S3ImputedStability.RData")
#load("data/imputed/S2ImputedStability.RData")
```

### Follow-up: Time Scales

#### Daily

Preparing the data for the time scale follow-up, which combines the common variables of all three studies on a daily level. Here, we:

1.  Select the variables for all relevant analysis (i.e., imputation, 3MPCA, and validation) across all three studies.
2.  Create the combined dataset in the correct format (long format with all missed time points as NAs).
3.  Impute the data and save the imputed datasets for later recall.

```{r MiDailyPrep}
#################################################################
##                    Dataframe Preparation                    ##
#################################################################
dtMiMainDaily <- rbind(
  dtS1Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S1") %>% 
    mutate(across(!TID & !study, as.numeric)),
  dtS2Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S2"),
  dtS3Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S3")
) %>%
  group_by(study, PID) %>%
  mutate(ID = cur_group_id()) %>%
  ungroup %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  rowwise() %>%
  mutate(
    InteractionDum = sum(IntergroupContact, IngroupContact, na.rm = TRUE),
    InteractionDum = if_else(InteractionDum > 0, 1, InteractionDum)
  ) %>%
  ungroup() %>%
  group_by(ID, date, study) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>% # contact dum should be summarized as sum()
  ungroup %>%
  group_by(study) %>%
  mutate(TIDnum = as.numeric(factor(date))) %>%
  ungroup %>%
  select(ID,
         study,
         date,
         everything(),
         -PID,
         -starts_with("ResponseId")) %>%
  as.data.frame %>%
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., ID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(ID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  mutate(study = replace_na(study, calc_mode(study))) %>%
  ungroup %>%
  group_by(study, TIDnum) %>%
  mutate(across(c("date"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate_if(is.numeric, ~ ifelse(is.nan(.), NA, .)) %>%
  as.data.frame 
```

```{r DailyImp}
#################################################################
##               Imputation at Daily Aggregation               ##
#################################################################
# MiMainDaily <-
#   amelia(
#     dtMiMainDaily,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("date", "study", "IntergroupContact", "IngroupContact"), #"PID",
#     #lags = names(dtMiMainDaily)[!names(dtMiMainDaily) %in% idVars],
#     #lags = names(dtMiMainDaily)[names(dtMiMainDaily) %in%varNamInMiMainRed],
#     #noms = names(dtMiMainDaily)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMainDaily))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiMainDaily, file = "data/imputed/MainDailyImputed.RData")
load("data/imputed/MainDailyImputed.RData")

# # Stability to imputations:
# set.seed(123)
# MiMainDailyStability <-
#   amelia(
#     dtMiMainDaily,
#     m = 20,
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("date", "study", "IntergroupContact", "IngroupContact"), #"PID",
#     #lags = names(dtMiMainDaily)[!names(dtMiMainDaily) %in% idVars],
#     #lags = names(dtMiMainDaily)[names(dtMiMainDaily) %in%varNamInMiMainRed],
#     #noms = names(dtMiMainDaily)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMainDaily))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiMainDailyStability, file = "data/imputed/MainDailyImputedStability.RData")
load("data/imputed/MainDailyImputedStability.RData")
```

#### Weekly

Preparing the data for the time scale follow-up, which combines the common variables of all three studies on a weekly level. Here, we:

1.  Select the variables for all relevant analysis (i.e., imputation, 3MPCA, and validation) across all three studies.
2.  Create the combined dataset in the correct format (long format with all missed time points as NAs).
3.  Impute the data and save the imputed datasets for later recall.

```{r MiWeeklyPrep}
dtMiMainWeeekly <- rbind(
  dtS1Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S1") %>% 
    mutate(across(!TID & !study, as.numeric)),
  dtS2Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S2"),
  dtS3Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S3")
) %>%
  group_by(study, PID) %>%
  mutate(ID = cur_group_id()) %>%
  ungroup %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  rowwise() %>%
  mutate(
    InteractionDum = sum(IntergroupContact, IngroupContact, na.rm = TRUE),
    InteractionDum = if_else(InteractionDum > 0, 1, InteractionDum)
  ) %>%
  ungroup() %>%
  group_by(ID, week, study) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ungroup %>%
  group_by(study) %>%
  mutate(TIDnum = as.numeric(factor(week))) %>%
  ungroup %>%
  select(ID,
         study,
         week,
         everything(),
         -PID,
         -starts_with("ResponseId")) %>%
  as.data.frame %>%
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., ID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(ID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  mutate(study = replace_na(study, calc_mode(study))) %>%
  ungroup %>%
  group_by(study, TIDnum) %>%
  mutate(across(c("week"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate_if(is.numeric, ~ ifelse(is.nan(.), NA, .)) %>%
  as.data.frame 
```

```{r WeeklyImp}
##################################################################
##               Imputation at Weekly Aggregation               ##
##################################################################
# MiMainWeekly <-
#   amelia(
#     dtMiMainWeeekly,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("week", "study", "IntergroupContact", "IngroupContact"), #"PID",
#     #lags = names(dtMiMainWeeekly)[!names(dtMiMainWeeekly) %in% idVars],
#     #lags = names(dtMiMainWeeekly)[names(dtMiMainWeeekly) %in%varNamInMiMainRed],
#     #noms = names(dtMiMainWeeekly)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMainWeeekly))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiMainWeekly, file = "data/imputed/MainWeeklyImputed.RData")
load("data/imputed/MainWeeklyImputed.RData")

# # Stability to imputations:
# set.seed(123)
# MiMainWeeklyStability <-
#   amelia(
#     dtMiMainWeeekly,
#     m = 20,
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("week", "study", "IntergroupContact", "IngroupContact"), #"PID",
#     #lags = names(dtMiMainWeeekly)[!names(dtMiMainWeeekly) %in% idVars],
#     #lags = names(dtMiMainWeeekly)[names(dtMiMainWeeekly) %in%varNamInMiMainRed],
#     #noms = names(dtMiMainWeeekly)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMainWeeekly))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiMainWeeklyStability, file = "data/imputed/MainWeeklyImputedStability.RData")
load("data/imputed/MainWeeklyImputedStability.RData")
```

### Follow-up: Response Type

#### Interaction Responses

```{r MiInteractionPrep}
#################################################################
##                    Dataframe Preparation                    ##
#################################################################

>>>>

Feature-based clustering has the advantage of being extremely flexible when it comes to dealing with real-world human data. Human data is commonly noisy, incomplete, and non-stationary. Many descriptive dimension-reduction, modeling, and raw time-series clustering procedures will require complete or stationary data from the researcher, and are thus currently not well-suited to deal with messy intensive-longitudinal data collected by many social science researchers.

We used the following five-step procedure to arrive at a stable, reproducible, and meaningful differentiation of participants ESM trajectories:

1. Variable selection
2. Feature extraction
3. (Feature selection)
4. Clustering
5. Visualization, interpretation, and validation

We begin by selecting the variables, which we would like to include in the clustering procedure. For the clustering of time-series characteristics we focus on variables that are specific to the ESM measurements (i.e., variables collected during the various daily dairy pings). This means, that variables from the pre- and post-test are excluded from the clustering procedure. While the variables can in theory be added as additional features, they are not the focus of this manuscript.

In our case, we begin by collecting the variables that are in the ESM measurements of all three studies, in order to build the most powerful dataset for the main analysis. We then additionally, divide the variables by their response type and by study to check for cluster differences in the validation phase:

1. *Main Analysis*: Variables across all three data sets
2. *Validation*: Variables by response type (interaction-specific or not)
3. *Validation*: Variables by study

```{r Preparation of Variable Names}
varNamS123Aux <- varNames %>%
  filter(
    aux != 0,
    studyS1 == "S1",
    studyS2 == "S2",
    studyS3 == "S3"
  ) %>%
  select(varNam) %>%
  pull
varNamS1Aux <- varNames %>%
  filter(
    aux != 0,
    studyS1 == "S1"
  ) %>%
  select(varNam) %>%
  pull
varNamS2Aux <- varNames %>%
  filter(
    aux != 0,
    studyS2 == "S2"
  ) %>%
  select(varNam) %>%
  pull
varNamS3Aux <- varNames %>%
  filter(
    aux != 0,
    studyS3 == "S3"
  ) %>%
  select(varNam) %>%
  pull

@@

varNamS123MIPsbl <- c(
  paste(varNamS123MI, rep(".pre", length(varNamS123MI)), sep = ""),
  varNamS123MI,
  paste(varNamS123MI, rep(".post", length(varNamS123MI)), sep = "")
)

@@

```{r variable names for all analyses}
# ID Variables (just to re-iterate)
idVars <- idVars
